\documentclass[sigconf,nonacm]{acmart}
\settopmatter{printacmref=false}
\setcopyright{none}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{microtype}
\graphicspath{{images/}}
\title{SynVulCommit: Validated LLM-Based Synthetic Commit Generation for Python Vulnerability Detection}
\author{Wassim Bejaoui}
\affiliation{\institution{University of Passau}\department{Faculty of Computer Science and Mathematics}\city{Passau}\country{Germany}}
\email{wassim.bejaoui@uni-passau.de}
\author{Sofian Yadir}
\affiliation{\institution{University of Passau}\department{Faculty of Computer Science and Mathematics}\city{Passau}\country{Germany}}
\email{sofian.yadir@uni-passau.de}
\begin{document}
\begin{abstract}
Machine-learning vulnerability detection depends on labeled code corpora, but real vulnerability-fixing commits are costly to mine and difficult to balance across weakness categories. This paper presents SynVulCommit, a provider-agnostic pipeline for generating Python vulnerability-fix commit pairs across seven VUDENC-compatible Common Weakness Enumeration (CWE) categories. The pipeline combines deterministic quota planning, CWE-specific structural checks, Bandit and Semgrep analysis, a second-stage large language model (LLM) reviewer, and exact, abstract-syntax-tree, and token-shingle duplicate rejection. The final verified window-balanced corpus contains 1,205 accepted pairs. From this corpus we freeze a balanced 1,043-pair subset with 149 synthetic commits per CWE and compare it with real VUDENC data under three training conditions: real-only, synthetic-only, and mixed real-plus-synthetic. We evaluate eight model variants from the previous labs: LSTM, multilayer perceptron (MLP), Random Forest, and convolutional neural network (CNN) with Word2Vec features, plus LSTM and CNN variants with CodeBERT and GraphCodeBERT embeddings. All models are evaluated on the same held-out real VUDENC test split. Synthetic-only training remains weaker than real-only training, showing that validated synthetic commits do not automatically match the real-data distribution. However, mixed training improves the best MLP result to a mean macro-F1 of 0.7161, the strongest overall score. These results support SynVulCommit as a controlled data-generation and augmentation framework, while showing that validation, diversity, and downstream representation must be designed together.
\end{abstract}
\maketitle
\input{paper_body}
\input{references}
\end{document}
