\begin{thebibliography}{12}

\bibitem{vudenc}
Laura Wartschinski, Yannic Noller, Thomas Vogel, Timo Kehrer, and Lars Grunske.
2022.
\newblock VUDENC: Vulnerability Detection with Deep Learning on a Natural Codebase for Python.
\newblock \emph{Information and Software Technology} 144 (2022), 106809.
\newblock https://doi.org/10.1016/j.infsof.2021.106809

\bibitem{vuldeepecker}
Zhen Li, Deqing Zou, Shouhuai Xu, Xinyu Ou, Hai Jin, Sujuan Wang, Zhijun Deng, and Yuyi Zhong.
2018.
\newblock VulDeePecker: A Deep Learning-Based System for Vulnerability Detection.
\newblock In \emph{Proceedings of the Network and Distributed System Security Symposium}.
\newblock https://doi.org/10.14722/ndss.2018.23158

\bibitem{russell2018}
Rebecca Russell, Louis Kim, Lei Hamilton, Tom Lazovich, Jacob Harer, Onur Ozdemir, Paul M. Ellingwood, and Marc McConley.
2018.
\newblock Automated Vulnerability Detection in Source Code Using Deep Representation Learning.
\newblock In \emph{2018 17th IEEE International Conference on Machine Learning and Applications}.
\newblock https://doi.org/10.1109/ICMLA.2018.00120

\bibitem{sysevr}
Zhen Li, Deqing Zou, Shouhuai Xu, Hai Jin, Yawei Zhu, and Zhaoxuan Chen.
2022.
\newblock SySeVR: A Framework for Using Deep Learning to Detect Software Vulnerabilities.
\newblock \emph{IEEE Transactions on Dependable and Secure Computing} 19, 4 (2022), 2244--2258.
\newblock https://doi.org/10.1109/TDSC.2021.3051525

\bibitem{devign}
Yaqin Zhou, Shangqing Liu, Jing Kai Siow, Xiaoning Du, and Yang Liu.
2019.
\newblock Devign: Effective Vulnerability Identification by Learning Comprehensive Program Semantics via Graph Neural Networks.
\newblock In \emph{Advances in Neural Information Processing Systems}.

\bibitem{bigvul}
Jiahao Fan, Yi Li, Shaohua Wang, and Tien N. Nguyen.
2020.
\newblock A C/C++ Code Vulnerability Dataset with Code Changes and CVE Summaries.
\newblock In \emph{Proceedings of the 17th International Conference on Mining Software Repositories}, 508--512.
\newblock https://doi.org/10.1145/3379597.3387501

\bibitem{chakraborty2022}
Saikat Chakraborty, Rahul Krishna, Yangruibo Ding, and Baishakhi Ray.
2022.
\newblock Deep Learning Based Vulnerability Detection: Are We There Yet?
\newblock \emph{IEEE Transactions on Software Engineering} 48, 9 (2022), 3280--3296.
\newblock https://doi.org/10.1109/TSE.2021.3087402

\bibitem{codebert}
Zhangyin Feng, Daya Guo, Duyu Tang, Nan Duan, Xiaocheng Feng, Ming Gong, Linjun Shou, Bing Qin, Ting Liu, Daxin Jiang, and Ming Zhou.
2020.
\newblock CodeBERT: A Pre-Trained Model for Programming and Natural Languages.
\newblock In \emph{Findings of the Association for Computational Linguistics: EMNLP 2020}, 1536--1547.
\newblock https://doi.org/10.18653/v1/2020.findings-emnlp.139

\bibitem{graphcodebert}
Daya Guo, Shuo Ren, Shuai Lu, Zhangyin Feng, Duyu Tang, Shujie Liu, Long Zhou, Nan Duan, Alexey Svyatkovskiy, Shengyu Fu, Michele Tufano, Shao Kun Deng, Colin Clement, and Ming Zhou.
2021.
\newblock GraphCodeBERT: Pre-Training Code Representations with Data Flow.
\newblock In \emph{International Conference on Learning Representations}.

\bibitem{vulberta}
Hazim Hanif and Sergio Maffeis.
2022.
\newblock VulBERTa: Simplified Source Code Pre-Training for Vulnerability Detection.
\newblock In \emph{2022 International Joint Conference on Neural Networks}, 1--8.
\newblock https://doi.org/10.1109/IJCNN55064.2022.9892280

\bibitem{pearce2022}
Hammond Pearce, Baleegh Ahmad, Benjamin Tan, Brendan Dolan-Gavitt, and Ramesh Karri.
2022.
\newblock Asleep at the Keyboard? Assessing the Security of GitHub Copilot's Code Contributions.
\newblock In \emph{2022 IEEE Symposium on Security and Privacy}, 754--768.
\newblock https://doi.org/10.1109/SP46214.2022.9833571

\bibitem{deng2024}
Xiao Deng, Fuyao Duan, Rui Xie, Wei Ye, and Shikun Zhang.
2024.
\newblock Improving Long-Tail Vulnerability Detection Through Data Augmentation Based on Large Language Models.
\newblock In \emph{2024 IEEE International Conference on Software Maintenance and Evolution}, 262--274.
\newblock https://doi.org/10.1109/ICSME58944.2024.00033

\end{thebibliography}
